Malacology: A Programmable Storage System

### 2017-03-10 paper/9_conclusion.tex
Adds sentence related to Popper
fixes #107

We thank the EuroSys reviewers for their hard work, attentiveness, and
genuinely helpful suggestions. We also thank Mahesh Balakrishnan for
championing and shepherding the paper. This work was partially funded by the
Center for Research in Open Source
Software\footnote{\url{http://cross.ucsc.edu}}, the DOE Award
DE-SC0016074, and the NSF Award 1450488.

\textbf{Note}: this paper follows The Popper
Convention~\cite{jimenez_popper_2016}. The Popper
Convention\footnote{\url{http://falsifiable.us}} is equivalent to
the ACM's Result and Artifiact Review and Badging procedures.
\includegraphics[width=3.5mm]{figures/popper.png}

>>>>

We thank the EuroSys reviewers for their hard work, attentiveness, and
genuinely helpful suggestions. We especially thank Mahesh Balakrishnan for
shepherding the paper. This work was partially funded by the
Center for Research in Open Source
Software\footnote{\url{http://cross.ucsc.edu}}, the DOE Award
DE-SC0016074, and the NSF Award 1450488.

\textbf{Note}: this paper follows The Popper
Convention\footnote{\url{http://falsifiable.us}}~\cite{jimenez_popper_2016}. All 
the experiments presented here are available on the repository associated to 
this 
article\footnote{\url{https://github.com/michaelsevilla/malacology-popper/tree/v2.1}}. 
For every figure, a \texttt{[source]} link points to a Jupyter notebook that 
shows the analysis from where the graph was obtained; its parent folder contains 
all the associated artifacts.
